### 2015-10-07 untitled.tex
edited untitled.tex

Nevertheless, Theorem 5 in \cite{Raj:suspension1991} can be useful for handling self-suspending task systems should there exist \emph{efficient} schedulability tests for the corresponding deferrable task systems or the period enforcer algorithm. However, such tests have not been found yet and the development of a precise and efficient schedulability test for self-suspending tasks remains an open problem.

>>>>

Nevertheless, Theorem 5 in \cite{Raj:suspension1991} can be useful for handling self-suspending task systems if there exist \emph{efficient} schedulability tests for the corresponding deferrable task systems or the period enforcer algorithm. However, such tests have not been found yet and the development of a precise and efficient schedulability test for self-suspending tasks remains an open problem.
